\documentclass{article}
%%%%%%%%%%%%%
% Loads packages
%%%%%%%%%%%%%
\usepackage[table]{xcolor}
\usepackage[utf8]{inputenc}
\usepackage[colorlinks=true,linkcolor=blue]{hyperref}
\usepackage{geometry} %package needed to set margins
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{mdframed}
\usepackage{tikz}
\usepackage{amsfonts}

\usepackage{listings}% http://ctan.org/pkg/listings
\lstset{
  basicstyle=\ttfamily,
  mathescape
}


\pagestyle{fancy}
\fancyhf{}
\chead{\textbf{Homework 3}}
\lhead{Math 213, Spring 2026}
\rhead{Due Wednesday, 2/11 at 9:00am}

%%%%%%%%%%%%%
% Sets margins
%%%%%%%%%%%%%
\newgeometry{left=1.5in,right=1in,top=1in,bottom=1in}
\setlength\headsep{3pt}

%%%%%%%%%%%%%
% Creates problem and solution environments
%%%%%%%%%%%%%

% Solution Environment
\newenvironment{solution}{\begin{proof}[Solution]}{\end{proof}}

% Problem Environment
\newenvironment{problem}[1]
    {\begin{mdframed}[default]
    \textbf{Problem #1:}
    }
    {\end{mdframed}
    }
    
%%%%%%%%%%%
% Custom Commands
%%%%%%%%%%%
\newcommand{\gOne}{\cellcolor{green!50!white} 1}
\newcommand{\rZero}{\cellcolor{red!50!white} 0}

\begin{document}

\begin{problem}{\S 3.1: 2}
Determine which characteristics of an algorithm described in the text the following procedures have and which they lack.
\begin{enumerate}
    \item[(a)]
    \begin{verbatim}
        procedure double(n: positive integer)
        while n > 0
            n := 2n
    \end{verbatim}
    \item[(b)]
    \begin{verbatim}
        procedure divide(n: positive integer)
        while n >= 0
            m : = 1/n
            n := n-1
    \end{verbatim}
    \item[(c)]
    \begin{verbatim}
        procedure sum(n: positive integer)
        sum := 0
        while i < 10
            sum := sum + i
    \end{verbatim}
    \item[(d)]
    \begin{verbatim}
        procedure choose(a,b: integers)
        x := either a or b
    \end{verbatim}
\end{enumerate}
\end{problem}

\begin{problem}{\S 3.1: 24}
Describe an algorithm that determines whether a function from a finite set to another finite set is one-to-one.
\end{problem}

\begin{problem}{\S 3.1: 52(a,d)}
Use the greedy algorithm to make change using quarters, dimes, nickels, and pennies for
\begin{enumerate}
    \item[(a)] 87 cents.
    \item[(d)] 33 cents.
\end{enumerate}
\end{problem}

\begin{problem}{\S 3.1: 54(a,d)}
Use the greedy algorithm to make change using quarters, dimes, and pennies (but no nickels) for
\begin{enumerate}
    \item[(a)] 87 cents.
    \item[(d)] 33 cents.
\end{enumerate}
\end{problem}

\begin{problem}{\S 3.2: 2(a,b,e,f)}
Determine whether each of these functions is $O(x^2)$:
\begin{enumerate}
    \item[(a)] $f(x) = 17x + 11$.
    \item[(b)] $f(x) = x^2 + 1000$.
    \item[(e)] $f(x) = 2^x$.
    \item[(f)] $f(x) = \lfloor x \rfloor \cdot \lceil x \rceil$.
\end{enumerate}
\end{problem}

\begin{problem}{\S 3.2: 8}
Find the least integer $n$ such that $f(x)$ is $O(x^n)$ for each of these functions.
\begin{enumerate}
    \item[(a)] $f(x) = 2x^2 + x^3\log{x}$.
    \item[(b)] $f(x) = 3x^5 + (\log{x})^4$.
    \item[(c)] $f(x) = (x^4+x^2+1)/(x^4+1)$.
    \item[(d)] $f(x) = (x^3+5\log{x})/(x^4+1)$.
\end{enumerate}
\end{problem}

\begin{problem}{\S 3.2: 17}
Suppose that $f(x)$, $g(x)$, and $h(x)$ are functions such that $f(x)$ is $O(g(x))$ and $g(x)$ is $O(h(x))$. Show that $f(x)$ is $O(h(x))$.
\end{problem}

\begin{problem}{\S 3.2: 26}
Give a big-$O$ estimate for each of these functions. For the function $g$ in your estimate $f(x)$ is $O(g(x))$, use a simple function $g$ of the smallest order.
\begin{enumerate}
    \item[(a)] $f(x) = (n^3+n^2\log{n})(\log{n}+1) + (17\log{n} + 19)(n^3+2)$.
    \item[(b)] $f(x) = (2^n + n^2)(n^3 + 3^n)$.
    \item[(c)] $f(x) = (n^n + n2^n + 5^n)(n!+5^n)$.
\end{enumerate}
\end{problem}

\begin{problem}{\S 3.2: 28(a,b,c,d)}
Determine whether each of the following functions is $\Omega(x)$ and whether it is $\Theta(x)$.
\begin{enumerate}
    \item[(a)] $f(x) = 10$.
    \item[(b)] $f(x) = 3x+7$.
    \item[(c)] $f(x) = x^2 + x + 1$.
    \item[(d)] $f(x) = 5\log{x}$.
\end{enumerate}
\end{problem}

\begin{problem}{Extra}
Explain what it means for a function to be
\begin{enumerate}
    \item[(a)] $O(1)$.
    \item[(b)] $\Omega(1)$.
    \item[(c)] $\Theta(1)$.
\end{enumerate}
\end{problem}

\begin{problem}{\S 5.1: 4}
Let $P(n)$ be the statement that $1^3 + 2^3 + \cdots + n^3 = (n(n+1)/2)^2$ for the positive integer $n$.
\begin{enumerate}
    \item[(a)] What is the statement $P(1)$?
    \item[(b)] Show that $P(1)$ is true, completing the basis step of the proof.
    \item[(c)] What is the inductive hypothesis?
    \item[(d)] What do you need to prove in the inductive step?
    \item[(e)] Complete the inductive step, identifying where you use the inductive hypothesis.
    \item[(f)] Explain why these steps show that this formula is true whenever $n$ is a positive integer.
\end{enumerate}
\end{problem}

\begin{problem}{\S 5.1: 6}
Prove that $1 \cdot 1! + 2 \cdot 2! + \cdots + n \cdot n! = (n+1)!-1$ whenever $n$ is a positive integer.
\end{problem}

\begin{problem}{\S 5.1: 8}
Prove that $2 - 2 \cdot 7 + 2 \cdot 7^2 - \cdots + 2(-7)^n = (1-(-7)^{n+1})/4$ whenever $n$ is a nonnegative integer.
\end{problem}

\end{document}