\documentclass{article}
%%%%%%%%%%%%%
% Loads packages
%%%%%%%%%%%%%
\usepackage[table]{xcolor}
\usepackage[utf8]{inputenc}
\usepackage[colorlinks=true,linkcolor=blue]{hyperref}
\usepackage{geometry} %package needed to set margins
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{mdframed}
\usepackage{tikz}
\usepackage{amsfonts}

\usepackage{listings}% http://ctan.org/pkg/listings
\lstset{
  basicstyle=\ttfamily,
  mathescape
}


\pagestyle{fancy}
\fancyhf{}
\chead{\textbf{Homework 4}}
\lhead{Math 213, Spring 2026}
\rhead{Due Wednesday, 2/25 at 9:00am}

%%%%%%%%%%%%%
% Sets margins
%%%%%%%%%%%%%
\newgeometry{left=1.5in,right=1in,top=1in,bottom=1in}
\setlength\headsep{3pt}

%%%%%%%%%%%%%
% Creates problem and solution environments
%%%%%%%%%%%%%

% Solution Environment
\newenvironment{solution}{\begin{proof}[Solution]}{\end{proof}}

% Problem Environment
\newenvironment{problem}[1]
    {\begin{mdframed}[default]
    \textbf{Problem #1:}
    }
    {\end{mdframed}
    }
    
%%%%%%%%%%%
% Custom Commands
%%%%%%%%%%%
\newcommand{\gOne}{\cellcolor{green!50!white} 1}
\newcommand{\rZero}{\cellcolor{red!50!white} 0}

\begin{document}

\begin{problem}{\S 5.1: 20}
Prove that $3^n < n!$ if $n$ is an integer greater than $6$.
\end{problem}

\begin{problem}{\S 5.1: 34}
Prove that $6$ divides $n^3 - n$ whenever $n$ is a nonnegative integer.
\end{problem}

\begin{problem}{\S 5.1: 49}
What is wrong with this ``proof'' that all horses are the same color?

\vspace{3mm}
\noindent Let $P(n)$ be the proposition that all the horses in a set of $n$ horses are the same color.

\vspace{2mm}
\noindent \emph{Basis Step:} Clearly, $P(1)$ is true.

\vspace{2mm}
\noindent \emph{Inductive Step:} Assume that $P(k)$ is true, so that all the horses in any set of $k$ horses are the same color. Consider any $k+1$ horses: number these horses as $1, 2, 3, \dots, k, k+1$. Now the first $k$ of these horses all must have the same color. Because the set of the first $k$ horses and the set of the last $k$ horses overlap, all $k+1$ must be the same color. This shows that $P(k+1)$ is true and finishes the proof by induction.
\end{problem}

\begin{problem}{\S 5.1: 51}
What is wrong with this ``proof''?

\vspace{3mm}
\noindent ``\emph{Theorem}'': For every positive integer $n$, if $x$ and $y$ are positive integers with $\textrm{max}(x,y) = n$, then $x = y$.

\vspace{2mm}
\noindent \emph{Basis Step:} Suppose that $n=1$. If $\textrm{max}(x,y)=1$ and $x$ and $y$ are positive integers, we have $x = 1$ and $y = 1$.

\vspace{2mm}
\noindent \emph{Inductive Step:} Let $k$ be a positive integer. Assume that whenever $\textrm{max}(x,y) = k$ and $x$ and $y$ are positive integers, then $x = y$. Now let $\textrm{max}(x,y) = k+1$, where $x$ and $y$ are positive integers. Then $\textrm{max}(x-1,y-1) = k$, so by the inductive hypothesis $x-1 = y-1$. It follows that $x = y$, completing the inductive step.
\end{problem}

\begin{problem}{\S 5.2: 8}
Suppose that a store offers gift certificates in denominations of $25$ and $40$ dollars. Determine the possible total amounts you can form using these gift certificates. Prove your answer using strong induction.
\end{problem}

\begin{problem}{\S 5.2: 10}
Assume that a chocolate bar consists of $n$ squares arranged in a rectangular pattern. The entire bar, a smaller rectangular piece of the bar, can be broken along on a vertical or horizontal line separating the squares. Assuming that only one piece can be broken at a time, determine how many breaks you must successively make to break the bar into $n$ separate squares. Use strong induction to prove your answer.
\end{problem}

\begin{problem}{\S 6.1: 8}
How many different three-letter initials with none of the letters repeated can people have?
\end{problem}

\begin{problem}{\S 6.1: 14}
How many bit strings of length $n$, where $n$ is a positive integer, start and end with $1$s?
\end{problem}

\begin{problem}{\S 6.1: 16}
How many strings are there of four lowercase letters that have the letter $x$ in them?
\end{problem}

\begin{problem}{\S 6.1: 26}
How many strings of four decimal digits
\begin{enumerate}
    \item[(a)] do not contain the same digit twice?
    \item[(b)] end with an even digit?
    \item[(c)] have exactly three digits that are $9$s?
\end{enumerate}
\end{problem}

\begin{problem}{\S 6.1: 30}
How many license plates can be made using either three uppercase English letters followed by three digits or four uppercase English letters followed by two digits?
\end{problem}

\begin{problem}{\S 6.1: 36}
How many functions are there from the set $\{1, 2, \dots, n \}$, where $n$ is a positive integer, to the set $\{ 0, 1 \}$?
\end{problem}

\begin{problem}{\S 6.1: 37}
How many functions are there from the set $\{ 1, 2, \dots, n \}$, where $n$ is a positive integer, to the set $\{ 0, 1 \}$
\begin{enumerate}
    \item[(a)] that are one-to-one?
    \item[(b)] that assign $0$ to both $1$ and $n$?
    \item[(c)] that assign $1$ to exactly one of the positive integers less than $n$?
\end{enumerate}
\end{problem}

\begin{problem}{\S 6.1: 40}
How many subsets of a set with $100$ elements have more than one element?
\end{problem}

\begin{problem}{\S 6.1: 44}
How many ways are there to seat four of a group of ten people around a circular table where two seatings are considered the same when everyone has the same immediate left and immediate right neighbor?
\end{problem}


\end{document}