\documentclass[12pt]{article}
\usepackage{fullpage, amsmath, amssymb, amsthm, amscd, setspace, bm, graphicx, indentfirst, multirow, tikz, enumerate, verbatim, appendix}

\usepackage{adjustbox,amsfonts,array,graphicx,booktabs,tabularx,multirow,multicol,stmaryrd, tabu}
\usepackage[utf8]{inputenc}
\usepackage{cite}
\usepackage{hyperref}
\usetikzlibrary{arrows.meta}
\title{Math 418, Spring 2025 -- Homework 10}
\date{}
\setlength{\parskip}{0.5cm}
\setlength{\parindent}{0cm}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}[theorem]{Definition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}

\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\U}{\mathcal{U}}
\newcommand{\B}{\mathcal{B}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\real}{\textrm{Re }}
\newcommand{\imag}{\textrm{Im }}
\newcommand{\deriv}[2]{\frac{d #1}{d #2}}
\newcommand{\sig}[1]{\sum_{#1 =1}^\infty}
\newcommand{\un}[1]{\bigcup_{#1 =1}^\infty}
\newcommand{\inter}[1]{\bigcap_{#1 =1}^\infty}
\newcommand{\cyc}[2]{\genfrac{[}{]}{0pt}{}{#1}{#2}}
\newcommand{\px}[2]{\genfrac{\{}{\}}{0pt}{}{#1}{#2}}
\newcommand{\wh}[1]{\widehat{#1}}
\newcommand{\del}{\partial}
\newcommand{\st}{ \; \big | \:}
\newcommand{\ba}{\overline}
\newcommand{\Int}{\mathrm{Int}}
\newcommand{\Cl}{\mathrm{Cl}}
\newcommand{\rel}{\mathrm{rel}}
\newcommand{\Hom}{\text{Hom}}
\newcommand{\End}{\text{End}}
\newcommand{\Mat}{\text{Mat}}
\newcommand{\Aut}{\text{Aut}}
\newcommand{\Mor}{\text{Mor}}
\newcommand{\Ind}{\text{Ind}}
\newcommand{\Irr}{\text{Irr}}
\newcommand{\Gal}{\text{Gal}}
\newcommand{\Fix}{\text{Fix}}
\renewcommand{\char}{\text{char }}
\newcommand{\vect}[1]{\boldsymbol{#1}}
\newcommand{\mfk}[1]{\mathfrak{#1}}
\newcommand{\wt}{\text{wt}}
\newcommand{\vx}[1]{\mathtt{#1}}
%\renewcommand{\wt}[1]{\mathtt{#1}}
\begin{document} \maketitle
\vspace{-80pt}

\textbf{Due:} Wednesday, May 7th, at 9:00am via Gradescope.

\textbf{Instructions:} Students should complete and submit all problems. Textbook problems are from Dummit and Foote, \emph{Abstract Algebra, 3rd Edition}. All assertions require proof, unless otherwise stated. Typesetting your homework using LaTeX is recommended, and will gain you 1 bonus point per assignment.

\begin{enumerate}

\item[1.] Let $k$ be an algebraically closed field, and consider the polynomial ring $k[x,y]$.  
  \begin{enumerate}
  \item Let $V$ be the $x$-axis, i.e.~$V = V(y)$. Prove that $V$ is irreducible. [Hint: Show a prime ideal is radical.]
  
  \item Prove that $V = V(x - y)$ is irreducible. 
  
  \item Prove that $S = \{(a,a) \in k^2 |a \neq 1\}$ is \emph{not} an algebraic variety if $k = \C$.

  \item What is the decomposition of $V = V(x^2 - y^2)$ into irreducibles?  \textbf{Warning:} The answer depends on $k$!
  \end{enumerate}

\item[2.] \textbf{Dummit and Foote \#15.1.2} Show that each of the following rings are not Noetherian by exhibiting an explicit infinite increasing chain of ideals:

\begin{enumerate}
\item the ring of continuous real valued functions on $[0, 1]$

\item the ring of all functions from any infinite set $X$ to $\Z/2\Z$.

\end{enumerate}

\item[3.] \textbf{Dummit and Foote \#15.1.20} \textit{If $f$ and $g$ are irreducible polynomials in $k[x, y]$ that are not associates (do not divide each other), show that $V((f, g))$ is either $\emptyset$ or a finite set in $k^2$.} [Hint: If $(f, g) \ne (1)$, show $(f, g)$ contains a nonzero polynomial in $k[x]$ (and similarly a nonzero polynomial in $k[y]$) by letting $R = k[x], F = k(x)$, and applying Gauss's Lemma to show $f$ and $g$ are relatively prime in $F[y]$.]

\item[4.] \textbf{Dummit and Foote \#15.2.2} Let $I$ and $J$ be ideals in the ring $R$. Prove the following statements:
\begin{enumerate}
\item If $I^k\subseteq J$ for some $k\ge 1$, then $\sqrt{I}\subseteq\sqrt{J}$.

\item If $I^k\subseteq J\subseteq I$ for some $k\ge 1$, then $\sqrt{I}=\sqrt{J}$.

\item $\sqrt{IJ} = \sqrt{I\cap J} = \sqrt{I}\cap\sqrt{J}$.

\item $\sqrt{\sqrt{I}} = \sqrt{I}$.

\item $\sqrt{I}+\sqrt{J} \subseteq \sqrt{I+J}$ and $\sqrt{I+J} = \sqrt{\sqrt{I}+\sqrt{J}}$.

\end{enumerate}

\item[5.] \textbf{Dummit and Foote \#15.2.3} \textit{Prove that the intersection of two radical ideals is again a radical ideal.}

\item[6.] \textbf{Dummit and Foote \#15.2.5} \textit{If $I = (xy, (x - y)z) \subseteq k[x, y, z]$ prove that $\sqrt{I} = (xy, xz, yz)$. For this ideal prove
\emph{directly} that $V(I) = V(\sqrt{I})$, that $V(I)$ is not irreducible, and that $\sqrt{I}$ is not prime.}

\item[7.] \textbf{Cox, Little, and O'Shea \#8.2.3} \textit{In this exercise, we will study how lines in $\R^n$ relate to points at infinity in $P^n(\R)$. We will use the decomposition $P^n(\R) = \R^n \cup P^{n-1}(\R)$. Given a line $L$ in $\R^n$, we can parametrize $L$ by the formula $a + bt$, where $a\in L$ and $b$ is a nonzero vector parallel to $L$. In coordinates, we write this parametrization as $(a_1+b_1t,\ldots,a_n+b_nt)$.}

\begin{enumerate}
    \item[(a)] We can regard $L$ as lying in $P^n(\R)$ using the homogeneous coordinates 
    \[
    [1 : a_1 + b_1t : \cdots a_n + b_nt].
    \]
    To find out what happens as $t\to\pm\infty$ divide by $t$ to obtain
    \[
    \left[\frac{1}{t} : \frac{a_1}{t} + b_1 : \cdots \frac{a_n}{t} + b_n\right].
    \]
    As $t\to\pm\infty$, what point of $H=P^{n-1}(\R)$ do you get?

    \item[(b)] The line $L$ will have many parametrizations. Show that the point of $P^{n-1}(\R)$ given by part (a) is the same for all parametrizations of $L$. Hint (from the book): Two nonzero vectors are parallel if and only if one is a scalar multiple of the other.

    \item[(c)]  Parts (a) and (b) show that a line $L$ in $\R^n$ has a well-defined point at infinity in $H = P^{n-1}(\R)$. Show that two lines in $\R^n$ are parallel if and only if they have the same point at infinity.
\end{enumerate}


\item[8.] \textbf{Cox, Little, and O'Shea \#8.2.7} \textit{In this exercise, we will study when a nonhomogeneous polynomial has a well-defined zero set in $P^n(k)$. Let $k$ be an infinite field. We will show that if $f\in k[x_0,..., x_n]$ is not homogeneous, but $f$ vanishes on all homogeneous coordinates of some $p\in P^n(k)$, then each of the homogeneous components $f_i$ of $f$ (see Definition 6 of Chapter 7, Section 1) must vanish at $p$.}

\begin{enumerate}
    \item[(a)] Write $f$ as a sum of its homogeneous components $f = \sum_i f_i$. If $p = (a_0,\ldots,a_n)$ then show that
    \[
    f(\lambda a_0,\ldots, \lambda a_n) = \sum_i f_i(\lambda a_0,\ldots, \lambda a_n) = \sum_i \lambda^i f(a_0,\ldots, a_n)
    \]

    \item[(b)] Deduce that if $f$ vanishes for all nonzero $\lambda\in k$, then $f_i(a_0,\ldots,a_n)=0$ for all $i$
\end{enumerate}

\end{enumerate}

\end{document}
